IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/related.tex
Removing performance trashing to JSFlow

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accommodate the entirety of JavaScript's
semantics). Moreover, the runtime performance cost are sometimes too high, e.g.,
higher than 100\%~\cite{JSFlow}.  Alternatively, coarse-grained
approaches to security have also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.

@@

Our definition of isomorphism of information flow control languages in
Section~\ref{sec:concrete} is closely related to the idea of
\emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
although as our system is deterministic, we do not use the theory in any
deep way.

>>>>

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accommodate the entirety of JavaScript's
semantics~\cite{JSFlow}).
%Moreover, the runtime performance cost are sometimes too high, e.g.,
%higher than 100\%~\cite{JSFlow}.
Alternatively, coarse-grained
approaches to security have also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.

@@

%Our definition of isomorphism of information flow control languages in
%Section~\ref{sec:concrete} is closely related to the idea of
%\emph{bisimulation}~\cite{Milner:1989:CC:534666} and process calculi,
%although as our system is deterministic, we do not use the theory in any
%deep way.
